---
title: "A/B Test"
author: ""
date: "3/12/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r libraries, echo=FALSE, warning=FALSE}
library(pacman)
p_load(dplyr)
p_load(ggplot2)
p_load(tidyverse)
p_load(lubridate)
p_load(summarytools)
p_load(pwr)
p_load(pacman)
p_load(kableExtra)
p_load(tidyr)
p_load(readr)
p_load(tsibble)
p_load(Hmisc)
p_load(funModeling)
p_load(reshape)

```

```{r set-options, echo=FALSE, cache=FALSE}
options(width = 1800)
knitr::opts_chunk$set(fig.width=12, fig.height=8) 
```


```{r importing}
## Import
df <- read.csv("data/events.csv")
```

```{r Variable overview}
df%>%head()%>% kable() %>%
  kable_styling(full_width = F, position = "left") %>%
  row_spec(0, color = "white", background = "#566573")

```

```{r}
glimpse(df)
summary(df)

```
```{r}
##Analyze Dataframe 
dim(df)
```

```{r}

##Frequency of the variables
freq(df$event_name)
```

### Data Cleaning ####
Duplicates removal
Filtering by important events
Formating of data date types

```{r Data Cleaning}
df <- df %>% distinct()
df$event_timestamp = as_datetime(df$event_timestamp)
df$user_first_touch_timestamp = as_datetime(df$user_first_touch_timestamp)
df <- df %>%
  filter(event_timestamp >= user_first_touch_timestamp & event_name %in% c("event_4", "event_1", "event_6", "event_12", "event_3"))



```

### Multiple Boardings
These table is created to check users with more than 1 boarding event in their register. 
```{r Multiple Boardings}
multiple_boardings <- df %>%
  group_by(user_pseudo_id, event_name) %>%
  summarise(count = n()) %>%
  pivot_wider(names_from = event_name, values_from = count, values_fill = 0)%>%
  filter(boarding_finished >= 2 | first_open != 1)


```

```{r}
df <- df %>% 
  filter(!user_pseudo_id %in% multiple_boardings$user_pseudo_id)

```
### Data Splitting 
The dataset is divided by dates, from the first four weeks is design phase. 
From February 3rd to March 29th is experiment phase. 

```{r Data Splitting}
design <- df%>%
  filter(between(user_first_touch_timestamp, as_datetime("2020-01-06"), as_datetime("2020-02-03")) & between(event_timestamp, as_datetime("2020-01-06"), as_datetime("2020-02-03")))
design$toweek <- as.Date(design$user_first_touch_timestamp) + days(-1) 

experiment <- df%>%
  filter(between(user_first_touch_timestamp, as_datetime("2020-02-03"), as_datetime("2020-03-30")) 
         & between(event_timestamp, as_datetime("2020-02-03"), as_datetime("2020-03-30")))
experiment$toweek <- as.Date(experiment$user_first_touch_timestamp) + days(-1) 

```
### Design EDA
```{r Distinct users}
design %>%
  group_by(event_name) %>%
  summarise(distinct_users = length(unique(user_pseudo_id))) %>%
  arrange(desc(distinct_users))


```
## top 10 Number of distinct users per country

```{r warning=FALSE, message=FALSE}
design %>%
  group_by(country) %>%
  summarise(distinct_users = length(unique(user_pseudo_id))) %>%
  arrange(desc(distinct_users))%>%
  head(10)%>%
  ggplot(., aes(country, distinct_users))+
  geom_col(aes(reorder(country, distinct_users)))+
  theme_classic()+
  labs(title = "Number of users by target Events")+
  coord_flip()+
  geom_label(aes(label=distinct_users))

```
## Plot of users per week (From jan.6 to feb.2 - 4 complete weeks)

```{r warning=FALSE, message=FALSE}
design %>% 
  group_by(wk = week(floor_date(as.Date(toweek), unit="week")), event_name)%>%
  summarise(usercount=n())%>%
  ggplot(.,aes(wk, usercount, color=event_name))+
  geom_point()+
  geom_line()+
  theme_classic()+
  scale_x_continuous("Week number", limits = c(1, 4)) 

```
## Faceted plot with total average (88k)

```{r warning=FALSE, message=FALSE}
design %>% 
  group_by(wk = week(floor_date(as.Date(toweek), unit="week")), event_name)%>%
  summarise(usercount=n())%>%
  ggplot(.,aes(wk, usercount, color=event_name))+
  geom_col(aes(fill=event_name))+
  geom_hline(aes(yintercept=mean(usercount)), 
             color = "black", linetype='dashed')+
  theme_classic()+
  theme(legend.position='none')+
  facet_wrap(~event_name)
```

### KPI Calculation
```{r}
pre_test_base <- design %>% 
  group_by(weeks = week(floor_date(as.Date(toweek), unit="week")), user_pseudo_id, event_name) %>%
  summarise( count = if_else(n()>0, 1, 0)) %>%
  pivot_wider( names_from = event_name, values_from = count, values_fill = 0)

pre_test_kpi <- colMeans(pre_test_base[,3:7])
```

```{r}
pre_test_base %>%
  group_by(weeks)%>%
  summarise(event_4 = mean(event_4),event_1 = mean(event_1), event_6 = mean(event_6), event_3 = mean(event_3), event_12 = mean(event_12))%>%
  gather("event_4", "event_1", "event_6", "event_12", "event_3" ,key=event_name, value= "counts" )%>%
  ggplot(aes(x= weeks, y = counts, col = event_name  )) + geom_point() + geom_line()

```
### Power Analysis 
```{r Power Calculation}
power_calculation_t <- function(uplift_an, sig_level,kpi_v) { 
  pwr.t.test.sample.size<- as.data.frame(
    do.call( "cbind", lapply(1:length(sig_level), function(i){
      sapply(1:length(uplift_an), function(j){
        variant <- (uplift_an[j] + 1) * kpi_v
        baseline <- ES.h( variant, kpi_v)
        pwr.t.test( d=baseline,
                     n=,
                     sig.level=sig_level[i],
                     power=0.8,
                     alternative= "greater") $n})})))
  
  table_format<- function(sample_size_table, sig_level, uplift_an){
    colnames(sample_size_table)<- paste(sig_level,"Significance Level")
    ftg<- cbind(uplift_an, sample_size_table)
    rfg <- cbind(melt(ftg, id = "uplift_an"), significance_level = rep(sig_level, each = length(uplift_an)))
    rfg <- rfg[-c(2)]
    names(rfg)[2] <-"samplesize"
    rfg$required_weeks <- rfg$samplesize/(length(pre_test_base$first_open)/(length(unique(pre_test_base$weeks))))
    return(rfg)
  }
  
  return(table_format(pwr.t.test.sample.size, sig_level, uplift_an))
}
```

```{r Bonferroni Correction}
bonferroni_correction <- function(alpha, no_variants){
  p_adjusted <- alpha/no_variants
  return (p_adjusted)
}


```
```{r Power Analysis Results}
sig <- 0.05
uplift <-seq(0.005, 0.1, 0.005)


sample_size_2_groups<- power_calculation_t(uplift ,sig , min(colMeans(pre_test_base[,4:7])))
sample_size_3_groups<- power_calculation_t(uplift,bonferroni_correction(sig,3),min(colMeans(pre_test_base[,3:7])))

ggplot(sample_size_2_groups, aes(samplesize, uplift, size = required_weeks, color = as.factor(required_weeks))) +geom_point() + ylab("uplift") + xlab("sample size")
ggplot(sample_size_3_groups, aes(samplesize, uplift, size = required_weeks, color = as.factor(required_weeks))) +geom_point() + ylab("uplift") + xlab("sample size")




```
```{r Ef. size boarding_finished}
pwr.2p.test( h= , 
             n= 157263.489,
             sig.level= 0.5 ,
             power=0.8,
             alternative= "greater")
h
```
```{r Ef. size other KPIs}
pwr.t.test(  d= , 
             n= 99749.128,
             sig.level= 0.01666667 ,
             power= 0.8,
             alternative= "greater")
d
```
### Experiment Phase
##users groups loading and adding to the experiment data_set

```{r User Groups Sorting}
users_groups <- read.csv("users_groups.csv")
groups_variant <- experiment %>% inner_join(users_groups, by = c("user_pseudo_id" = "user_pseudo_id"))



```
```{r KPI Calculation}
experiment_base <- groups_variant %>% 
  group_by(group_name, weeks = week(floor_date(as.Date(toweek), unit="week")), user_pseudo_id, event_name) %>%
  summarise(count = n()) %>%
  pivot_wider( names_from = event_name, values_from = count, values_fill = 0)

experiment_kpi <- experiment_base %>% 
  group_by(group_name)%>%
  summarise( users = sum(first_open), first_open = mean(first_open),boarding_finished = mean(boarding_finished), diagnosis_open_camera = mean(diagnosis_open_camera), calculator_calculate = mean(calculator_calculate), community_open_post = mean(community_open_post))

experiment_sum <- experiment_base %>% 
  group_by(group_name)%>%
  summarise( users = sum(first_open), first_open = sum(first_open),boarding_finished = sum(boarding_finished), diagnosis_open_camera = sum(diagnosis_open_camera), calculator_calculate = sum(calculator_calculate), community_open_post = sum(community_open_post))

experiment_base %>%
  group_by(group_name, weeks)%>%
  summarise(boarding_finished = mean(boarding_finished))%>%
  ggplot(aes(x= weeks, y = boarding_finished, col = group_name  )) + geom_point() + geom_line()

```
```{r}
group_a_diagnosis_open_camera <- t.test(x= experiment_base$diagnosis_open_camera[experiment_base$group_name=='variant_a'],y= experiment_base$diagnosis_open_camera[experiment_base$group_name=='control_group'], alternative = 'greater')
group_a_calculator_calculate <- t.test(x= experiment_base$calculator_calculate[experiment_base$group_name=='variant_a'], y= experiment_base$calculator_calculate[experiment_base$group_name=='control_group'], alternative = 'greater')
group_a_community_open_post <- t.test(x= experiment_base$community_open_post[experiment_base$group_name=='variant_a'], y= experiment_base$community_open_post[experiment_base$group_name=='control_group'], alternative = 'greater')
group_a_boarding_finished <- prop.test(x=c(126557, 123626), n=c(161846, 161746), alternative='greater', conf.level = 0.95 )

conf_interval_a <- function(x) {
  p <- x/161846
  n <- 161846
  z <- qnorm(0.95)
  p + c(-1,1)*z*sqrt(p*(1-p)/n)
}




group_b_diagnosis_open_camera <- t.test(x= experiment_base$diagnosis_open_camera[experiment_base$group_name=='variant_b'],y= experiment_base$diagnosis_open_camera[experiment_base$group_name=='control_group'], alternative = 'greater')
group_b_calculator_calculate <- t.test(x= experiment_base$calculator_calculate[experiment_base$group_name=='variant_b'], y= experiment_base$calculator_calculate[experiment_base$group_name=='control_group'], alternative = 'greater')
group_b_community_open_post <- t.test(x= experiment_base$community_open_post[experiment_base$group_name=='variant_b'], y= experiment_base$community_open_post[experiment_base$group_name=='control_group'], alternative = 'greater')
group_b_boarding_finished <- prop.test(x=c(125419, 123626), n=c(162390, 161746), alternative='greater', conf.level = 0.95 )

conf_interval_b <- function(x) {
  p <- x/162390
  n <- 162390
  z <- qnorm(0.95)
  p + c(-1,1)*z*sqrt(p*(1-p)/n)
}

conf_interval_b(25172)



eff_size_group_a_diagnosis_open_camera <-ES.h((((0.4898793 - 0.4884387) + 1) * 0.4884387), 0.4884387)
eff_size_group_a_calculator_calculate <- ES.h((((0.1720339 - 0.1684740) + 1) * 0.1684740), 0.1684740)
eff_size_group_a_community_open_post <- ES.h((((0.1546038 - 0.1534814) + 1) * 0.1534814), 0.1534814)
eff_size_group_a_boarding_finished <- ES.h((((0.7819594 - 0.7643218) + 1) * 0.7643218), 0.7643218)

```

